---
title: "Midpoint Deliverable"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "./scripts/")
```
### Introduction to our project
We are business, economics, and computational finance majors, and we felt that the field of housing markets intersected all of our major-related interests, so we chose to focus on it for our project. The data sets we decided to use come from Zillow. Zillow regularly gathers information about all of the homes listed for sale on their website and makes it publicly available, and we decided to make use of several pieces of it. 
The first lists the median housing prices across the nation according to different regional categories. It can be used to answer questions about how house prices vary by geographic region, as well as how they've changed over the past ten years. The second lists the average number of days a listing stays on Zillow by region. This can be used to examine changes in the speed with which houses sell in different areas.
The pricing data was downloaded [here](https://data.world/zillow-data/median-list-price/) and the listing data was downloaded [here](https://data.world/zillow-data/days-on-zillow).

### Summary Code
```{r summary info, echo = FALSE, message = FALSE, warning = FALSE}
source("./summary-information.R")
```
Looking at the dataset, which displays US city median house prices, we can note
a few pieces of interesting information. According to the data, the city with
the highest median house price in 2017 was `r get_summary_info(city_price_data)[1]`,
while the city with the lowest median house price was `r get_summary_info(city_price_data)[2]`. 
The average median US city house price was 
`r get_summary_info(city_price_data)[3]` in 2017. These values demonstrate that
house price varies significantly depending on the city.
The median 2017 house price in New York, which is the largest city in the dataset,
was `r get_summary_info(city_price_data)[4]`. The median 2017 house price in Winterset,
which is tied for the smallest city listed in the data, was `r get_summary_info(city_price_data)[5]`. This data suggests that the size of city
might be correlated with the price. 

### Aggregate Table
The table created displays the highest 15 listing prices for the data sets. The
grouping calculation was done with "RegionName" because that column is what 
identifies the location type of the data set (City). The 
"RegionName" column is present in every data set so that is why it is used. 
By using city to group, we can tell which cities have the highest prices.

<center><h3><b>Top 15 Cities by Median Price</b></h3></center>

```{r aggregate table, echo = FALSE,message = FALSE, warning = FALSE}
library("knitr")
library("kableExtra")
source("./aggregate_Table.R")
kable(
  aggregate_table(city_data), align = "c",
  col.names = c("City", "Median Price ($)")
  ) %>%
  kable_styling(font_size = 20) %>%
  kable_styling(latex_options = "scale_down") %>%
  row_spec(c(1,3,5,7,9,11,13,15), color = 'black', background = '#BFEFFF') %>%
  row_spec(c(2,4,6,8,10,12,14), color = 'white', background = '#236B8E')

```

One key insight from this table is that most of these listed cities are not
big, well-known cities. Another trend noticed is words like "island", "harbor",
and "beach" appearing in some of these city names, implying that a lot of the
most expensive cities are near bodies of water.

### Chart Number 1: Map
This map attempts to display the geographic spread of the data by placing a
marker at each city mentioned in the data set. The size of the marker is
scaled linearly on the median house price in September 2017
```{r city map, echo = FALSE, message = FALSE, warning = FALSE}
library("leaflet")
source("./first-chart.R")
map_maker(city_location)
```
As can be seen from the graph, the cities with the highest median house prices
in September 2017 (the last available date from the data) are largely clustered
around large coastal metropolis areas such as Seattle, New York, and Los
Angeles. This indicates a trend that larger cities have higher median house
prices.

### Chart Number 2: Bar Graph
This bar plot takes the average of the given median house prices at the
beginning of each year to illustrate annual changes in house price
```{r bar chart, echo = FALSE, message = FALSE, warning = FALSE}
source("./bar-chart.R")
bar_graph(city_data)
```

This bar graph shows how prices have dropped from 2010 to 2012. And prices have
risen from 2012 to 2017. Prices were slightly higher in 2017 than in 2010,
indicating a general trend that house prices increase.

### Chart Number 3: Line Graph
This line graph looks at the average number of days a house remains listed on Zillow by time, and it breaks the data down by region. It answers questions such as "When did houses take the longest time to sell?", and it will takes user input to decide which region to show. Below is an example of King County, and Washington as a whole.
```{r line graph, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 10}
source("./days-listed-line-chart.R")
line_graph("county", "king", "WA")
line_graph("state", "washington")
```
The graphs clearly show that over the years, selling a house has become a quicker process. Even more pronounced in the difference in time it takes to sell a house by season. Depending on the location, houses listed on Zillow in Winter and Fall can take nearly twice as long to sell as those listed in Spring and Summer.
