---
title: "index"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Summary Code

For each piece of Summary Info(1 x 5): Include the piece of information using in-line R code in the paragraph

## Aggregate Table

Introduces the table, explaining why the particular grouping calculation was performed
Displays well formatted column names
Successfully renders the table in the report using an appropriate package (e.g., don't just print
out the data frame)
Interprets information the table, honing in on important information
 
## Chart 1: Map

This map attempts to display the geographic spread of the data by placing a
marker at each city mentioned in the data set.
```{r city_map, echo = FALSE, message = FALSE}
library("leaflet")
source("scripts/first-chart.R")
city_map
```
As can be seen from the graph, the cities with the highest median house prices
in September 2017 (the last available date from the data) are largely clustered
around large coastal metropolis areas such as Seattle, New York, and Los
Angeles.

## Chart Number 2
description of what the chart attempts to answer/understand
Interprets information from the chart, honing in on important information

## Chart Number 3
description of what the chart attempts to answer/understand
Interprets information from the chart, honing in on important information
 